---
title: "Historical Tuition Costs"
subtitle: "Try Infinite Moon Reader"
author: "Tidy Tuesday"
date: "2020-03-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Historical Tuition Costs

The goal is to plot historical tuition averages, 
using data from [TidyTuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-03-10).
Refactor the code below as much as you want.
After each change in this document,
press <kbd>Cmd/Ctrl</kbd> + <kbd>S</kbd> to save
and refresh the preview.

```{r echo=FALSE, fig.width=8, fig.height=4}
library(tidyverse)

# {here} makes it easy to find files in projects!
raw_nces_csv <- here::here("data", "raw_nces.csv")

raw_nces <- read_csv(raw_nces_csv)

# tidy_tuition <- function(raw_tuition) {
#   raw_tuition
# }

all_school <- raw_nces %>% slice(2:21) %>% mutate(type = "All Institutions") %>%
  pivot_longer(names_to = "tuition_type", values_to = "tuition_cost", `All Constant`:`2 Year Current`) %>%
  select(type, year, everything()) %>%
  mutate_at(vars(tuition_cost, year), parse_number)


public_school <- raw_nces %>% slice(23:41) %>%
  mutate(
    year = if_else(year == "2015-16" & `All Constant` == "17,237","2016-17", year),
    type = "Public"
  ) %>%
  pivot_longer(names_to = "tuition_type", values_to = "tuition_cost", `All Constant`:`2 Year Current`) %>%
  select(type, year, everything()) %>%
  mutate_at(vars(tuition_cost, year), parse_number)

private_school <- raw_nces %>% slice(43:(n() - 1)) %>% mutate(type = "Private") %>%
  pivot_longer(names_to = "tuition_type", values_to = "tuition_cost", `All Constant`:`2 Year Current`) %>%
  select(type, year, everything()) %>%
  mutate_at(vars(tuition_cost, year), parse_number)


tuition <- bind_rows(all_school, public_school, private_school)

tuition %>%
  filter(year >= 2000, tuition_type == "4 Year Current") %>%
  ggplot() +
  aes(year, tuition_cost, color = type) +
  geom_point()
```


## Infinite Moon Reader

- To start **Infinite Moon Reader**, select it from the _Addins_ drop-down.

- To stop the live preview, restart your R session  
  
  _Hint: Use a keyboard shortcut!_
